---
title: "Statistical Methods: Assignment 10"
author: "Yiftach Kolb (5195763)"
output: pdf_document
---

## Exercise 1

First lets contstruct the data set:
groups 1 to 4 are: 'sp','p','sv','v'.

```{r}
library(nparcomp)
library(tidyverse)

sp <- c(3.56,3.41,3.2,3.75,3.58,3.88,3.49,3.18,3.9,3.35,3.12,3.9)
sv <- c(4.00,3.84,3.98,3.9,3.88,3.73,4.41,4.19,4.5,4.2,4.05,3.67)
p <-  c(2.81,2.89,3.75,3.3,3.84,3.58,3.89,3.29,3.45,3.6,3.4,3.3)
v <- c(3.85,2.96,3.75,3.6,3.44,3.29,4.04,3.89,4.2,3.6,3.9,3.6)

#group <- as.factor(rep(c(1:4), each=12))
group <- as.factor(rep(c("sp","p","sv","v"), each=12))

score <- c(sp, p, sv, v)

mydata <- tibble(score, group)

mymat <- rbind(c(0,0,1,-1),
               c(1,0,-1,0),
               c(0,1,0,-1))
colnames(mymat) <- c("sp", "p", "sv", "v")
rownames(mymat) <- c("v:sv", "sv:sp", "v:p")


```

Idealy we could use a custom contrast matrix which looks like this:

```{r}
mymat %>% print
```

But I couldn't figure out how to use it in the functions. So
instead, I used the Tukey matrix, which basically compares all
pairs, including ones we don't need.

So first here is the result from 'nparcomp':

```{r}
nparcomp(score ~ group, data = mydata, asy.method = "mult.t",  plot.simci = TRUE, type="Tukey")
```

From the result we see that we can reject "V = SV" and assume that
"SV" tends to be larger. We also reject "SV = SP" and SV tends to be
larger than SP. 
V = P cannot be rejected.

To clarify, by V = P etc. I mean the null hypothesis is that their
relative effects are 0.5 (npartest) or are equal to each other
(mctp)

now repeat the same procedure but with mctp.

```{r}
mctp(score ~ group, data = mydata, type = "Tukey", asy.method = "mult.t", plot.simci = TRUE)
```

The results are similar:
SV = V: rejected
SV = P: rejected
V = P: not rejected.

SV tends to be larger than SP and V, V, and P cannot be
distinguished (p value is 0.55).
